Personality and political beliefs across the lifespan

### 2019-12-01 scripts/manuscript.Rmd
updates on results section

```{r correlations, include = FALSE}
set.seed=180
cor_conservatism <- corr.test(untidy$economic_conservatism, untidy$social_conservatism)
cor_conservatism

untidy_cor <- untidy %>% 
  select(-c(1:6))
cor_conservatism_ocean <- corr.test(untidy_cor)
cor_conservatism_ocean
```

@@

```{r figure1, fig.cap= "Generally, older adults rated themselves higher on each of the big five personality traits than young adults. This sample was unexpectedly introverted."}
ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +
  geom_smooth(se=FALSE, method = "lm")+
  labs(title = "Social Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
       x= "How strongly participants identify with the personality trait", y = "Social Conservatism", 
       color = "Personality Trait")+
  theme_minimal()+
  scale_color_viridis_d() +
  facet_wrap(~conservatism_type)
```

@@

To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be r = 0.65.

>>>>

```{r correlations, echo = FALSE, results = "asis"}
set.seed=180
cor_conservatism <- corr.test(untidy$economic_conservatism, untidy$social_conservatism)
cor_conservatism

untidy_cor <- untidy %>% 
  select(-c(1:6)) %>% 
  rename('Social conservatism' = 'social_conservatism',
         'Economic conservatism' = 'economic_conservatism',
         'Openness to experiences' = 'openness_to_experiences',
         'Emotional stability' = 'emotional_stability')
cor_conservatism_ocean <- round(cor(untidy_cor),2)
upper_s<-cor_conservatism_ocean
upper_s[upper.tri(cor_conservatism_ocean)]<-""
upper_s<-as.data.frame(upper_s) %>%
  apa_table(
    caption = "Correlation Matrix for Conservatism and Big Five Personality Traits",
  landscape = TRUE,
  font_size = "tiny")
```

@@

```{r figure1}
ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +
  geom_smooth(se=FALSE, method = "lm")+
  labs(title = "Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
       x= "How strongly participants identify with the personality trait", y = "Conservatism", 
       color = "Personality Trait")+
  theme_minimal()+
  scale_color_viridis_d() +
  facet_wrap(~conservatism_type)
```

@@

To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be r = 0.65. Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits.
